---
title: "Third Assignment"
author: "mittens@sk.com"
date: "Oct. 26th 2017"
output: 
  ioslides_presentation:
    smaller: true
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Synopsis

  The final project requires a shiny app and the presentation about that.
  
  Here, I built a simple neural net classifier with the sample iris dataset and try to figure out what is the name of your input data

## The Shiny App

  You can test my app published [here](https://mittens.shinyapps.io/Proj3/).
  Just click and type some numbers. You can also see some boxplot distributions of the features of the iris dataset by selecting dropdown box.

## The Model

  This is the code for building simple random forest classifier.
  Select only 90 observation from the total of 150 to training the model.

```{r, message=F, warning=F}
library(caret)
library(randomForest)
```

```{r, echo=T, warning=F}
train<-createDataPartition(iris$Species, p=0.6, list=F)
trainset<-iris[train,]
testset<-iris[-train,]

set.seed(2)
model_rf<-randomForest(Species~., data=trainset)

valid_rf<-predict(model_rf, trainset)
result_rf<-confusionMatrix(valid_rf, trainset$Species)
```

## The Model Result

```{r, fig.align='center', message=F, warning=F}
result_rf$overall
result_rf$byClass
```

## Test

  You can test the model's accuracy by the test set which is not included for the training set from the iris dataset.

```{r, echo=T, warning=F}
test_rf<-predict(model_rf, testset)
result_test_rf<-confusionMatrix(test_rf, testset$Species)
result_test_rf$overall
```

