---
title: "Third Assignment"
author: "mittens@sk.com"
date: "Oct. 26th 2017"
output: ioslides_presentation
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Synopsis

  The final project requires a shiny app and the presentation about that.
  
  Here, I built a simple neural net classifier with the sample iris dataset and try to figure out what is the name of your input data

## The Shiny App

  You can test my app published here. <link>
  Just click and type some numbers. You can also see some boxplot distributions of the features of the iris dataset by selecting dropdown box.

## The Model

  This is the code for building simple neural network classifier.
  Select only 90 observation from the total of 150 to training the model.

```{r, fig.align='center', message=F, warning=F}
library(caret)
train<-createDataPartition(iris$Species, p=0.6, list=F)
trainset<-iris[train,]
testset<-iris[-train,]

set.seed(2)
model_nn<-train(Species~., data=trainset, method='nnet', preProcess=c('center','scale'))
valid_nn<-predict(model_nn, trainset)
result_nn<-confusionMatrix(valid_nn, trainset$Species)
result_nn
```


## Test

  You can test the model's accuracy by the test set which is not included for the training set from the iris dataset.

```{r, fig.align='center', message=F, warning=F}

test_nn<-predict(model_nn, testset)
result_test_nn<-confusionMatrix(test_nn, testset$Species)
result_test_nn
```
